Regression

### 2018-02-08 paper/R/03_marektDescription.Rmd
change labels

rm(list=ls())
col <- brewer.pal(6,"Dark2")
source("func/functions.R")
```

@@

views <- views %>%
  mutate(site = ifelse(site=="bild.de","Bild.de",site),
       site = ifelse(site=="focus.de","FOCUS ONLINE",site),
       site = ifelse(site=="spiegel.de","SPIEGEL ONLINE",site),
       site = ifelse(site=="zeit.de","ZEIT ONLINE",site),
       site = ifelse(site=="tagesschau.de","Tagesschau.de",site),
       site = ifelse(site=="zdf.de","ZDF.de",site),
       site = ifelse(site=="welt.de","DIE WELT",site),
       site = ifelse(site=="n-tv.de","n-tv.de",site))

```{r}
p1 <- views %>%
  filter(date > as.POSIXct("2017-05-31")) %>%
  ggplot(aes(date, views, color=site)) +
  geom_line(show.legend = F) +
  geom_text_repel(data = views[views$date==max(views$date), ],
                  aes(date, views, label=site),
                  size=2.8, show.legend = F, seed = 1) +
  scale_x_date(limits = c(as.Date("2017-05-31"),as.Date("2018-02-15")),
               breaks = date_breaks("1 month"), 
               labels=date_format("%B %y", tz="CET")) +
  theme(
      #legend.position   = "none",
      legend.text       =  element_text(size=6),
      axis.text.y       = element_text(size = 8)
    ) +
  labs(x="", y="pageviews", color="", title = "", 
      caption = "Source: Alexa Internet, Inc. (www.alexa.com)" )

>>>>

rm(list=ls())
col <- brewer.pal(6,"Dark2")
```

@@

views <- views %>%
  mutate(site = ifelse(site=="bild.de","Bild.de",site),
       site = ifelse(site=="focus.de","FOCUS ONLINE",site),
       site = ifelse(site=="spiegel.de","SPIEGEL ONLINE",site),
       site = ifelse(site=="zeit.de","ZEIT ONLINE",site),
       site = ifelse(site=="tagesschau.de","Tagesschau.de",site),
       site = ifelse(site=="zdf.de","ZDF.de",site),
       site = ifelse(site=="welt.de","DIE WELT",site),
       site = ifelse(site=="n-tv.de","n-tv.de",site),
       site = ifelse(site=="deutschlandfunk.de", "DLF", site))

keepsite <- c("Tagesschau.de", "SPIEGEL ONLINE", "ZEIT ONLINE", 
              "Bild.de", "DIE WELT", "FOCUS ONLINE")
```

```{r}
p1 <- views %>%
  filter(date > as.POSIXct("2017-05-31")) %>%
  ggplot(aes(date, views, color=site)) +
  geom_line() +
  geom_text(data = views[views$date==max(views$date) &
                                 views$site %in% keepsite , ],
                  aes((date+3), views, label=site), hjust=0.1,
                  size=2.5, show.legend = F, check_overlap = T) +
  scale_x_date(limits = c(as.Date("2017-05-31"),as.Date("2018-02-16")),
               breaks = date_breaks("1 month"), 
               labels=date_format("%B %y", tz="CET")) +
  theme(
      legend.position   = "right",
      legend.text       =  element_text(size=6),
      axis.text.y       = element_text(size = 8)
    ) +
  labs(x="", y="pageviews", color="", title = "", 
      caption = "Source: Alexa Internet, Inc. (www.alexa.com)" )
